Documentation/overview Functional Limits of Agreement

### 2021-06-10 floa_doc.Rmd
Flowchart for old version completed

>>>>

#### Eingereichte Version (problematisch)

```{r echo = FALSE, warning = FALSE, message = FALSE}
library(DiagrammeR)

# (Nested) Randomized Cluster Bootstrap
#
# In the first stage (draw_clusters()), all curves of a single (random) subject
# are drawn. From this set, the (functional) mean is calculated. The process is
# repeated n.boot times (n.boot = number of bootstrap iterations)

grViz("digraph flowchart {

      # node definitions with substituted label text
      node [fontname = Helvetica, shape = rectangle]

      tab1 [label = '@@1']
      tab2 [label = '@@2']
      tab3 [label = '@@3']
      tab4 [label = '@@4']
      tab5 [label = '@@5']
      tab6 [label = '@@6']
      tab7 [label = '@@7']
      tab8 [label = '@@8']
      tab9 [label = '@@9']
      tab10 [label = '@@10']

      # edge definitions with the node IDs
      tab1 -> tab2
      tab2 -> tab3
      tab3 -> tab4
      tab3 -> tab5
      tab3 -> tab6
      tab4 -> tab7
      tab7 -> tab8
      tab8 -> tab9
      tab9 -> tab10
      }

      [1]: 'Time normalize curves of IMU - MC'
      [2]: 'Create difference curves IMU - MC'
      [3]: 'Convert difference curves to function data objects using Fourier series'
      [4]: 'floa_rcb '
      [5]: 'FLOAboot_2SD '
      [6]: 'floa_point'
      [7]: paste0('First stage', ':\\n ', 'draw_clusters', '\\n ', 'All strides from 11 subjects (randomly permuted)', '\\n ', 'are drawn with replacement')
      [8]: 'Functional mean for each cluster'
      [9]: paste0('Second stage', ':\\n ', 'Repeat the first stage 1000 times')
      [10]: 'Quantile'
      ")

```

Asymmetrische Limits of Agreement aus einem hierarchischen (zweistufigen) Bootstrap in Anlehnung an Davison & Hinkley (1997)

#### Vorschlag für verbesserte Variante
